Modeling potential JCPOA diversion scenarios with Cyclus

### 2018-05-04 paper.tex
update experiment

\section{The Experiment}
\subsection{The Fuel Cycle}
This work aims to assess the impact of the functional uncertainties of a
simple transition (see Figure \ref{fig:cycle}) inspired from the EG23 of the Screening And
Evaluation Group\cite{FCO}: a transition from light water reactors fleet loaded
with \glspl{UOX} fuel to a sodium fast reactors fleet loaded \glspl{MOX} fuel, considering an
$1\%/$y grows of the generated power (Figure \ref{fig:power}).
\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
  \centering
  \includegraphics[scale=0.31]{cycle.png}
  \caption{Illustration of the material flow between the different facilities,
  with in green each operational parameters associated with an
  uncertainty.}\label{fig:cycle}
\end{figure}

As illustrated on Figure \ref{fig:power}, the transition starts with a fleet
fully composed by \glspl{LWR} loaded with enriched \glspl{UOX} fuel. The actual
transition starts around year 35, with the deployment of \glspl{FBR}, loaded
with Mixed oxide fuel (MOX), consisting of plutonium blended with natural
uranium. Once the transition to a full \glspl{FBR} fleet is completed, the
\glspl{FBR} fleet is slowly replaced with \glspl{FBR} with a lower breeding
ratio.

@@

The plutonium, required for the \glspl{MOX} fabrication, is reprocessed from all
used fuel, at first only used UOX, then used MOX fuel as they start to be
available for reprocessing.

>>>>

\section{The Experiment}
\subsection{The Fuel Cycle}
This work aims to assess the impact of the functional uncertainties of a
simple transition as shown in Figure \ref{fig:cycle}, inspired from the EG23 fuel cycle of the Nuclear Fuel Cycle Evaluation and Screening Report\cite{FCO}: a transition from light water reactors fleet loaded
with \glspl{UOX} fuel to a sodium fast reactor fleet loaded \glspl{MOX} fuel, considering an
$1\%/$y growth of the generated power (Figure \ref{fig:power}).
\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
  \centering
  \includegraphics[scale=0.31]{cycle.png}
  \caption{Illustration of the material flow between the different facilities,
  with in green each operational parameters associated with an
  uncertainty.}\label{fig:cycle}
\end{figure}

As illustrated in Figure \ref{fig:power}, the transition starts with a fleet
fully composed of \glspl{LWR} loaded with enriched \glspl{UOX} fuel. The actual
transition starts around year 35, with the deployment of \glspl{FBR}, loaded
with \glspl{MOX}, consisting of plutonium blended with natural
uranium. Once the transition to a full \glspl{FBR} fleet is completed, the
\glspl{FBR} fleet is slowly replaced with \glspl{FBR} with a lower breeding
ratio.

@@

The plutonium, required for \glspl{MOX} fabrication, is reprocessed from all
used fuel. At first , it is sourced only from UOX, then used MOX fuel as it becomes
available for reprocessing.
